---
output: 
  pdf_document:
    latex_engine: xelatex
    number_sections: true
header-includes:
- \usepackage{graphicx}
- \usepackage{setspace}
- \usepackage{fancyhdr}
- \usepackage{enumitem}
- \usepackage{fontspec}
- \setmainfont[Ligatures=TeX,Scale=1.2, BoldFont={CormorantGaramond-Bold}, ItalicFont={CormorantGaramond-LightItalic}, BoldItalicFont={CormorantGaramond-BoldItalic}]{CormorantGaramond-Light}
---
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\begin{titlepage}
\begin{doublespace}
\center
\Huge
\text{UCLA}

\Large
\text{Statistics 141SL}

\text{Practice of Statistics Consulting}

\HRule 

\Huge
\bf{A Study on Sugar Streak}\\

\HRule

\Large
\begin{minipage}{0.4\textwidth}
\begin{flushleft}
\emph{Authors:}\\
\text{Youhee Kil, Yue Fei,} \\
\text{Suyao Hu, Xinru Fang}
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright}
\emph{Supervisor:}\\
\text{Prof. Esfandiari, Mahtash}
\end{flushright}
\end{minipage}\\[1.0cm]

\text{Winter 2017}\\[1.0cm]

\includegraphics[width=\linewidth]{uclaseal.jpg}
\normalsize
\end{doublespace}
\end{titlepage}

\newpage
\tableofcontents
\pagebreak

\section{Abstract}


\section{Introduction}


```{r,warning = FALSE,echo=FALSE, fig.width=5, fig.height=2}

```



```{r, echo=FALSE, fig.width=5, fig.height=2}

```


\section{Research Questions}

\begin{enumerate}
  \item{}
  \item{}
\end{enumerate}


\section{Research Process}


```{r warning = FALSE, echo=FALSE, fig.width=5, fig.height=2}

```



```{r warning = FALSE, echo=FALSE, fig.width=4, fig.height=2}

```

  
```{r warning = FALSE, echo=FALSE, fig.width=5, fig.height=4}

```

   
\section{Results}
  
\includegraphics{ODDS.png}
\includegraphics{result.png}


\section{Conclusion}

\section{Shortcomings and Future Study}

\section{References}


\section{Appendix}
\includegraphics{coefficients_1.png}

\includegraphics{coefficients_2.png}

\includegraphics{coefficients_3.png}